Full Title of Article\titlebreak This Title Has A Line Break

### 2021-09-02 Submission/Paper/ML4H/Paper.tex
added figure 1
added tfidf model stats

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{tabto}    
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{url}

@@

\paragraph{Dataset}
\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank. Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition.

@@

% Table 2 - Results
\begin{table*}[hbtp]
%   {\caption{TF-IDF Vector Features Correlation}}
  {\begin{tabular}{lccccccc}
    \toprule

    \bfseries Model & \bfseries AUCROC & \bfseries ACC & \bfseries Sensitivity & \bfseries Specificity & \bfseries FP & \bfseries FN & \bfseries Prediction Threshold \\ 
    Model 2 & 0.94 & 0.90 & 0.73 & 0.94 & __ & __ & 0.89 \\

    \bottomrule
  \end{tabular}}

\end{table*}

@@

@@

>>>>

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{tabto}    
\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{natbib}
\usepackage{url}

@@

\paragraph{Dataset}
\label{sec:Dataset} Our gold-standard dataset consisted of a cohort (N = 16,428) of patients from the Mass General Brigham (MGB) HealthCare (formerly Partner's Healthcare, comprising two major academic hospitals, community hospitals, and community health centers in the Boston area) system who were older than 60 years (as of July 13, 2021) and had APOE genotype (biggest genetic risk factor for dementia) data available from the BioBank. Each patients' EHR record was then annotated by neurologists using a web-based annotation tool (UI Interface in Appendix A) as 1) Yes, i.e., patient has CI; 2) No i.e., Patient does not have CI; and 3) Neither i.e., sequence has no information on patient’s cognition. 
% link
Appendix C shows examples of example sequences for all 3 classes.

@@

% Table 2 - Results
\begin{table}[hbtp]
  {\begin{tabular}{lcccccccc}
    \toprule 
    \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
    \midrule
    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.814 & 0.843 \\
    \bottomrule
  \end{tabular}}
  {\caption{F1 Scores for TF-IDF, Transformer}}
\end{table}

@@

\newpage

@@

\newpage

% Appendix C

\label{sec:AppendixC}
\section{Example Sequences} 
\includegraphics[width = 15cm, height = 5cm]{Figure-1.png}
\caption{Figure 1: Example Sequences}
